---
title: "Assigment 2"
author: "Alícia Chimeno Sarabia and Bruna"
date: "2023-12-02"
output:
  html_document: default
  pdf_document: default
---

# Libraries
```{r}
library(skimr)
library(car)
```

# Load dataset
```{r}
setwd("/Users/ali/Desktop/MASTER/SIM/proj2")
# aqui fica la teva ubi Bruna
df<-read.csv("customer.xls", sep=",")
```

# Data context
This dataset contains information about customers. Demographic data, 

# Data exploration

```{r}
dim(df)
names(df)
str(df)
#summary(df)
#skim(df)
```

## Variables description
In total, we have 21 variables related to demographic, services, and accountant data. One is the ID, three are numerical variables, and 17 are categorical (? binary) variables. We will conduct a descriptive analysis and a data quality report for each variable, considering aspects such as the number of missing values, errors, and the distribution or balance of the variable...
#### 1. customerID 

### Demographic data
#### 2. gender
Is a binary variable (female/male). 
```{r}
sum(is.na(df$gender))
table(df$gender)
barplot(table(df$gender), main = "Distribution of gender",xlab = "Gender",col = "skyblue")
```

#### 3. SeniorCitizen
Is a binary variable, YES/NO. 
```{r}
sum(is.na(df$SeniorCitizen))
table(df$SeniorCitizen)
barplot(table(df$SeniorCitizen), main = "Distribution of SeniorCitizen",xlab = "SeniorCitizen",col = "skyblue")
```

#### 4. Partner
It is a binary variable. Levels: Yes/No. 
```{r}
sum(is.na(df$Partner))
table(df$Partner)
barplot(table(df$Partner), main = "Distribution of Partner",xlab = "Partner",col = "skyblue")
```


#### 5. Dependents
It is a binary variable. Levels: Yes/No. 
```{r}
sum(is.na(df$Dependents))
table(df$Dependents)
barplot(table(df$Dependents), main = "Distribution of Dependents",xlab = "Dependents",col = "skyblue")

```

### Services of the costumer data
Services that each customer has signed up for :
#### 6. tenure
It is a numerical variable that indicates the duration, in months, that the customer has stayed with the company. 
```{r}

```

#### 7. PhoneService 
It is a binary variable. Levels: Yes/No. 
```{r}
sum(is.na(df$PhoneService))
table(df$PhoneService)
barplot(table(df$PhoneService), main = "Distribution of PhoneService",xlab = "PhoneService",col = "skyblue")
```

#### 8. MultipleLines
It is a binary variable. Levels: Yes/No. 
```{r}
sum(is.na(df$MultipleLines))
table(df$MultipleLines)
```

```{r}
# check inconsistencies
subset(df, MultipleLines == "Yes" & PhoneService == "No") 
```


#### 9. InternetService
It is a binary variable. Levels: Yes/No. 

```{r}
table(df$InternetService)
```

#### 10. OnlineSecurity
It is a factor variable with 3 levels: 
```{r}
table(df$OnlineSecurity)
```

```{r}
# Check concistency
sum(df$InternetService == "No")
sum(df$OnlineSecurity == "No internet service")
```


#### 11. OnlineBackup

#### 12. DeviceProtection

#### 13. TechSupport

#### 14. StreamingTV

#### 15. StreamingMovies


### Customer account data
#### 16. Contract

#### 17. PaperlessBilling
Is a binary variable. 

#### 18. PaymentMethod
Is a factor variable with 4 levels: 

#### 19. MonthlyCharges (numeric)

```{r}
summary(df$MonthlyCharges)
hist(df$MonthlyCharges,breaks=20)
```


```{r}
Boxplot(df$MonthlyCharges, main="Outlier analysis for MonthlyCharges")
sm <- summary(df$MonthlyCharges)
iqr <- sm["3rd Qu."] - sm["1st Qu."]
# Mild Outliers
mild_ub <- sm["3rd Qu."] + 1.5 * iqr
mild_lb <- sm["1st Qu."] - 1.5 * iqr
length(which(df$MonthlyCharges > mild_ub | df$MonthlyCharges < mild_lb)) # number of mild outliers

# Severe Outliers
severe_ub <- sm["3rd Qu."] + 3 * iqr
severe_lb <- sm["1st Qu."] - 3 * iqr
length(which(df$MonthlyCharges > severe_ub | df$MonthlyCharges < severe_lb)) # number of severe outliers

```


#### 20. TotalCharges (numeric)

```{r}
summary(df$TotalCharges)
hist(df$TotalCharges,breaks=20)
```


```{r}
Boxplot(df$TotalCharges, main="Outlier analysis for TotalCharges")
sm <- summary(df$TotalCharges)
iqr <- sm["3rd Qu."] - sm["1st Qu."]
# Mild Outliers
mild_ub <- sm["3rd Qu."] + 1.5 * iqr
mild_lb <- sm["1st Qu."] - 1.5 * iqr
length(which(df$TotalCharges > mild_ub | df$TotalCharges < mild_lb)) # number of mild outliers

# Severe Outliers
severe_ub <- sm["3rd Qu."] + 3 * iqr
severe_lb <- sm["1st Qu."] - 3 * iqr
length(which(df$TotalCharges > severe_ub | df$TotalCharges < severe_lb)) # number of severe outliers

```
### Target: 
#### 21. Churn
It is the target variable. It is binary, describes whether the customer churned or not (Yes or No). 


## Data preprocessing
### Recode variables into correct type
We shall reconvert the type of certain variables that are encoded with wrong type. First, we convert the character variables (except the ID) into factors.
```{r}
char_cols <- which(sapply(df, is.character))
df[, char_cols[-1]]<- lapply(df[, char_cols[-1]], as.factor) 
```

Also, we convert the numerical variable SeniorCitizen into a factor.  
```{r}
df$SeniorCitizen<- factor(df$SeniorCitizen)
```

```{r}
summary(df)
```

